Are you moving predictably?

### 2018-07-10 dokumentation/submission.tex
Hatte was vergessen :dash:

	\section{Preprocessing}\label{sec: proprocessing}
	In order to classify the given data into smaller test sets or mask different aspects, we have to perform some analysis.\\
	We observe that even though we have 124979 individual lines defining a movement, there is one line defining a \texttt{NotANumber}-exception and therefore gets neglected for further usage.	\\
	We provide the \texttt{testDataGenerator} python script. Through flags and input arguments, the script is able to create all test sets considered by our clustering and neural net approaches.\\
	We observe the following distribution over the whole dataset:\\
	\begin{figure}[H]
		\centering
		\setlength\tabcolsep{.2cm}
		\begin{tabular}{c|ccccccc}
			strata &  1   &   2   &   3   &  4   &  5   &  6   & $\Sigma$ \\ \hline
			abs   & 6963 & 52265 & 49404 & 8772 & 5536 & 2038 &  124978  \\
			\%   & 5.57 & 41.82 & 39.53 & 7.02 & 4.43 & 1.63 &   100
		\end{tabular}
		\label{table: distribution normal}
	\end{figure}
	We observe that there is an upper bound on equal distribution through strata 6. It has at most 2038 individual elements.

	In addition to the original paper we compute the value \texttt{ID}, which is used to combine movements considered to be from the same person.
	We consider two movements to coincide on the underlying person, if and only if they are consecutive in the original dataset and have the same strata, age and gender.
	\begin{figure}[H]
		\centering
		\setlength\tabcolsep{.2cm}
		\begin{tabular}{c|ccccccc}
			strata &  1   &   2   &   3   &  4   &  5   &  6  & $\Sigma$ \\ \hline
			abs   & 3153 & 23367 & 21418 & 3497 & 2083 & 595 &  54113   \\
			\%   & 5.83 & 43.18 & 39.58 & 6.46 & 3.85 & 1.1 &   100
		\end{tabular}
	\end{figure}
	So we also have through strata 6 an upper bound of 595 for equally distributed person vector data (see \Cref{subsec: person vector data}).

@@

	%TODO: recompute
	The size of larger nets in terms of neurons is counter-productive, since if we take 50 neurons per layer we have $14 \cdot 50^4 \cdot 6 \approxeq 525.000.000$ synapses for which the input data set would be to small to have sufficient training.\\

@@

		%	\bibitem{ref_lncs1}
		%	Author, F., Author, S.: Title of a proceedings paper. In: Editor,
		%	F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
		%	Springer, Heidelberg (2016). \doi{10.10007/1234567890}
		%	
		%	\bibitem{ref_book1}
		%	Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
		%	Location (1999)
		%	
		%	\bibitem{ref_proc1}
		%	Author, A.-B.: Contribution title. In: 9th International Proceedings
		%	on Proceedings, pp. 1--2. Publisher, Location (2010)
		%	
		%	\bibitem{ref_url1}
		%	LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
		%	Oct 2017
	\end{thebibliography}
\end{document}

>>>>

	\section{Preprocessing}\label{sec: proprocessing}
	In order to classify the given data into smaller test sets or mask different aspects, we have to perform some analysis.\\
	We observe that even though we have 124979 individual lines defining a movement, there is one line defining a \texttt{NotANumber}-exception and therefore gets neglected for further usage.	\\
	We provide the \texttt{testDataGenerator} python script. Through flags and input arguments, the script is able to create all test sets considered by our clustering and neural net approaches.\\
	We observe the following distribution over the whole dataset:\\
	\begin{figure}[H]
		\centering
		\setlength\tabcolsep{.2cm}
		\begin{tabular}{c|ccccccc}
			strata &  1   &   2   &   3   &  4   &  5   &  6   & $\Sigma$ \\ \hline
			abs   & 6963 & 52265 & 49404 & 8772 & 5536 & 2038 &  124978  \\
			\%   & 5.57 & 41.82 & 39.53 & 7.02 & 4.43 & 1.63 &   100
		\end{tabular}
		\label{table: distribution normal}
	\end{figure}
	We observe that there is an upper bound on equal distribution through strata 6. It has at most 2038 individual elements.
	Furthermore we have to make sure that  two different data points, which belong to the very same person, are assigned to the same cluster. To do so we compute the value \texttt{ID} which identifies each person and can be used to combine movements that are considered to be from the same person, i. e. two movements correspond with the very same person, if and only if they are consecutive in the original dataset and have the same strata, age and gender. This approach is taken since the surveys are concatenated sequentially and it is unlikely, that multiple consecutive movements with same strata, age, gender belong to two different persons.
	\begin{figure}[H]
		\centering
		\setlength\tabcolsep{.2cm}
		\begin{tabular}{c|ccccccc}
			strata &  1   &   2   &   3   &  4   &  5   &  6  & $\Sigma$ \\ \hline
			abs   & 3153 & 23367 & 21418 & 3497 & 2083 & 595 &  54113   \\
			\%   & 5.83 & 43.18 & 39.58 & 6.46 & 3.85 & 1.1 &   100
		\end{tabular}
	\end{figure}
	In Section \Cref{subsec: person vector data} we introduce vectors representing single persons. Since strata 6 is the smallest strata with 595 persons, it limits the size of an equally distributed dataset where each data point coincides with one person.

@@

	%TODO: recompute
	The size of larger nets in terms of neurons is counter-productive, since if we take 50 neurons per layer we have $14 \cdot 50^4 \cdot 6 \approxeq 525.000.000$ synapses for which the input data set would be too small to have sufficient training.\\

@@

	\end{thebibliography}
\end{document}
